An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-06-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
color change

  hamby252.plot.list[[1]] <- hamby252.cmps %>% ggplot() +
    geom_histogram(aes(x = cmps.max.m,
                       fill = as.factor(type_truth)), binwidth = 1) +
    labs(
      fill = "Comparison Type",
      x = expression(CMPS[max]),
      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
      subtitle = titlee
    ) +
    scale_x_continuous(breaks = seq(0, 27, 1)) +
    theme_bw() +
    theme(panel.grid.minor = element_blank()) +
    font("x.text", size = 6)

  hamby252.plot.list[[2]] <- hamby252.cmps %>% ggplot() +
    geom_histogram(aes(x = cmps.maxbar.m,
                       fill = as.factor(type_truth)), binwidth = 1) +
    labs(
      x = expression(bar(CMPS)[max]),
      fill = "Comparison Type",
      # title = expression(paste(
      #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
      # )),
      subtitle = titlee
    ) +
    scale_x_continuous(breaks = seq(0, 24, 1)) +
    theme_bw() +
    theme(panel.grid.minor = element_blank())

@@

  hamby44.plot.list[[1]] <- hamby44.cmps %>% ggplot() +
    geom_histogram(aes(x = cmps.max.m,
                       fill = as.factor(type_truth)), binwidth = 1) +
    labs(
      fill = "Comparison Type",
      x = expression(CMPS[max]),
      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
      subtitle = titlee
    ) +
    scale_x_continuous(breaks = seq(0, 27, 1)) +
    theme_bw() +
    theme(panel.grid.minor = element_blank()) +
    font("x.text", size = 6)

  hamby44.plot.list[[2]] <- hamby44.cmps %>% ggplot() +
    geom_histogram(aes(x = cmps.maxbar.m,
                       fill = as.factor(type_truth)), binwidth = 1) +
    labs(
      x = expression(bar(CMPS)[max]),
      fill = "Comparison Type",
      # title = expression(paste(
      #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
      # )),
      subtitle = titlee
    ) +
    scale_x_continuous(breaks = seq(0, 24, 1)) +
    theme_bw() +
    theme(panel.grid.minor = element_blank())

@@

As presented in the work of @cmps, researchers applied the CMPS method to one of the Hamby set scans (Hamby 252). In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44. Because the CMPS algorithm works with bullet signatures in our case, we conducted some data-processing: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann [@aoas] with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures. Note that researchers of @cmps used a different framework to obtain bullet signatures. However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.

@@

\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while fixing other parameters. In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`. We can see that the separation between KM comparisons and KNM comparisons is increased. This shows that the parameters used in the CMPS algorithm could potentially affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.

>>>>

  hamby252.plot.list[[1]] <- hamby252.cmps %>% ggplot() +
    geom_histogram(aes(x = cmps.max.m,
                       fill = as.factor(type_truth)), binwidth = 1) +
    labs(
      fill = "Comparison Type",
      x = expression(CMPS[max]),
      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
      subtitle = titlee
    ) +
    scale_x_continuous(breaks = seq(0, 27, 1)) +
    theme_bw() +
    theme(panel.grid.minor = element_blank()) +
    font("x.text", size = 6) +
    scale_fill_manual(values=c("darkorange", "darkgrey"))

  hamby252.plot.list[[2]] <- hamby252.cmps %>% ggplot() +
    geom_histogram(aes(x = cmps.maxbar.m,
                       fill = as.factor(type_truth)), binwidth = 1) +
    labs(
      x = expression(bar(CMPS)[max]),
      fill = "Comparison Type",
      # title = expression(paste(
      #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
      # )),
      subtitle = titlee
    ) +
    scale_x_continuous(breaks = seq(0, 24, 1)) +
    theme_bw() +
    theme(panel.grid.minor = element_blank()) +
    scale_fill_manual(values=c("darkorange", "darkgrey"))

@@

  hamby44.plot.list[[1]] <- hamby44.cmps %>% ggplot() +
    geom_histogram(aes(x = cmps.max.m,
                       fill = as.factor(type_truth)), binwidth = 1) +
    labs(
      fill = "Comparison Type",
      x = expression(CMPS[max]),
      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
      subtitle = titlee
    ) +
    scale_x_continuous(breaks = seq(0, 27, 1)) +
    theme_bw() +
    theme(panel.grid.minor = element_blank()) +
    font("x.text", size = 6)+
    scale_fill_manual(values=c("darkorange", "darkgrey"))

  hamby44.plot.list[[2]] <- hamby44.cmps %>% ggplot() +
    geom_histogram(aes(x = cmps.maxbar.m,
                       fill = as.factor(type_truth)), binwidth = 1) +
    labs(
      x = expression(bar(CMPS)[max]),
      fill = "Comparison Type",
      # title = expression(paste(
      #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
      # )),
      subtitle = titlee
    ) +
    scale_x_continuous(breaks = seq(0, 24, 1)) +
    theme_bw() +
    theme(panel.grid.minor = element_blank()) +
    scale_fill_manual(values=c("darkorange", "darkgrey"))

@@

As presented in the work of @cmps, researchers applied the CMPS method to one of the Hamby set scans (Hamby 252). In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44. Because the CMPS algorithm works with bullet signatures in our case, we conducted some data-processing: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by @aoas with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures. Note that researchers of @cmps used a different framework to obtain bullet signatures. However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.

@@

\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while adjusting other parameters. In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`. We can see that this results in an increased separation between KM comparisons and KNM comparisons. This shows that the parameters used in the CMPS algorithm could potentially affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
